Draft Visualizations for Semester Project

### 2018-11-30 Visualizations/Draft Visualizations Template.Rmd
Updated rcode
Monalisa_Rcode

>>>>

```
###Analzing the relationship between perceiving the negative impact of mental illness at previous workplace and the impact at current workplace

####Plotting the ggplot for the independent variable "Do you think that discussing a mental health disorder with previous employers would have negative consequences?"

```{r}
ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with previous employer resulting in negative consequences") + xlab("Response") + ylab("Count")
summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences.)

####Interpreting the results
From the above ggplot, we can observe that a majority of respondents(615) feel that discussing mental health disorders with some of their previous employers resulted in negative consequences for them. While a significant number of respondents responded that they do not know, we can conclude from the graph that the majority did experience negative consequences after discussing mental health disorders with their previous employers

###Plotting the ggplot for the dependent variable "Do you think that discussing a mental health disorder with your employer would have negative consequences?"

```{r}
ggplot(health, aes(x = health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)) + geom_bar() + ggtitle("Discussing mental health disorder with current employer resulting in negative consequences") + xlab("Response") + ylab("Count")
summary(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)

####Interpretation of results
From the above ggplot, we can see that a vast majority of respondents(487) are not sure if discussing mental health disorders with their current employers would have negative consequences; followed by about 438 respondents who do not think that it could lead to negative consequences

####Chi-squared test
```{r}
t1<-table(health$Do.you.think.that.discussing.a.mental.health.disorder.with.previous.employers.would.have.negative.consequences., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
chisq.test(t1)
```

####Interpret results
We can see that the p-value of the Chi-squared test is very small, meaning we can reject the hypothesis of independence. Thus there is a relationship between perceiving the negative impact of mental illness at previous workplace and the impact at current workplace
